Limb-darkening and exoplanets II: Choosing the Best Law for Minimum Bias Retrieval of Transit Parameters

### 2016-01-11 first_response_to_referee.txt

>> I would recommend adding a few sentences to the abstract to give a little more context 
>> for the paper. For example, something to the effect of: "Very precise measurements of 
>> exoplanet transit light curves enable limb darkening parameters to be fitted empirically, 
>> rather than fixed on theoretical model predictions that may have unknown systematic errors. 
>> However, even fitting for the limb darkening coefficients can introduce bias in the measured 
>> transit parameters depending on the chosen limb darkening model parameterization." I recommend 
>> adding this because because fitting for the coefficients directly is still a relatively new 
>> approach in this field, and it may not be obvious to everyone why you're not just using the 
>> standard nonlinear law.

We thank the referee for this suggestion. We have rewritten the first few sentences in the abstract 
in order to provide the suggested context to the paper.

>> There are several cases of very precise transit light curves where the limb darkening coefficients 
>> predicted from theoretical models does not provide a good fit to the data (Knutson et al. 2007, ApJ, 
>> 655, 564; Kreidberg et al. 2015, ApJ, 814, 66).  Please cite these in the introduction.

We have added the suggested citations to the discussion in the introduction.

@@

>> State in the text what time sampling you use for your model light curves, and how sensitive your 
>> results are to the choice of time sampling.

We have added the following at the end of the second paragraph in Section 3:

"$1000$ in-transit points and $400$ out-of-transit points were simulated per lightcurve, with the initial 
times perturbed by a small amount in order for the results to be independent of the exact points at which the lightcurve is sampled 
(which anyways our simulations show has a negligible effect given the large amount of sampled points)."

### 2016-01-11 which_law_2_use.tex
Added additional response. Now working on the rest.

\begin{abstract}
With the advent of very precise measurements of exoplanet transit lightcurves both from ground and space based observatories, it has been 
shown that it is now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. In 
addition, this strategy has been shown to give better results as fixing the coefficients to theoretical values can give rise to important yet unknown systematic 
errors, which directly impact the physical properties of the system derived from such lightcurves such as the exoplanet's radius, scaled 
semi-major axis and inclination. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are in fact better descriptions 
of model intensity profiles, which in principle could diminish the bias even further. In this work, we show that laws such as the logarithmic, 
square-root and three-parameter do a better job in general at retrieving the mentioned parameters from transit lightcurves than the widely 
used quadratic law and therefore we recommend using those instead. We also provide code to guide the decision of when to use each of 
the laws,  which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the so-called exponential 
law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
\end{abstract}

@@

As in EJ15, we simulate transit lightcurves for planets orbiting host stars with solar metallicity, 
gravity and microturbulent velocity, and $T_{\rm eff}$ between 3500 K and 9000 K, with the mentioned planet-to-star radius ratios, 
values of the scaled semi-major axis of 
$a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
impact parameters. The transits are simulated using a non-linear law in order to emulate ``real" intensity profiles, 
with the coefficients generated using the ATLAS models and the same methods as the ones used in EJ15 with the 
{\em Kepler} bandpass. The transits were then fitted using free limb-darkening coefficients.

>>>>

\begin{abstract}
With the advent of very precise measurements of exoplanet transit lightcurves both from ground and space based observatories, it has been 
shown that it is now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. 
This strategy has been shown to give better results as fixing the coefficients to theoretical values can give rise to important yet unknown systematic 
errors, which directly impact the physical properties of the system derived from such lightcurves such as the exoplanet's radius, scaled 
semi-major axis and inclination. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are in fact better descriptions 
of model intensity profiles, which in principle could diminish the bias even further. In this work, we show that laws such as the logarithmic, 
square-root and three-parameter do a better job in general at retrieving the mentioned parameters from transit lightcurves than the widely 
used quadratic law and therefore we recommend using those instead. We also provide code to guide the decision of when to use each of 
the laws,  which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the so-called exponential 
law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
\end{abstract}

@@

As in EJ15, we simulate transit lightcurves for planets orbiting host stars with solar metallicity, 
gravity and microturbulent velocity, and $T_{\rm eff}$ between 3500 K and 9000 K, with the mentioned planet-to-star 
radius ratios, values of the scaled semi-major axis of $a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
impact parameters. The transits are simulated using a non-linear law in order to emulate ``real" intensity profiles, 
with the coefficients generated using the ATLAS models and the same methods as the ones used in EJ15 with the 
{\em Kepler} bandpass. $1000$ in-transit points and $400$ out-of-transit points were simulated per lightcurve, with the initial 
times perturbed by a small amount in order for the results to be independent of the exact points at which the lightcurve is sampled 
(which anyways our simulations show has a negligible effect given the large amount of sampled points). The transits were then fitted 
using free limb-darkening coefficients.
